\vspace{-0.25em}\thetitle

### 2009-07-29 paper.tex
...

Our experimental methodology has three parts:
training, prediction and evaluation.
For training, we take a sample of network trace traffic and try to recover the model hypothesized in \Section{hypothesis} from it.
Next, we use the trained model to predict behaviors of a separate set of flows from the same trace, using only knowledge of a few initial packets of each flow.
Finally, we must evaluate the quality of these predictions by comparing them to the actual behavior of those flows.

It seems wise at this point to address the nature of prediction for highly nondeterministic phenomena like network traffic.
Brief reflection shows that one cannot hope to accurately predict the exact behavior of flows:
flows may exhibit the same initial behavior but subsequently behave quite differently.
The best we can do then is to predict a \emph{distribution} of possible outcomes given the observed initial behavior.
When compared with a specific outcome, such a prediction cannot be said to be ``wrong'' or ``right.''
How then can one measure the quality of a predicted distribution of outcomes?
This subtle and difficult issue is central to our evaluation methodology.

>>>>

Our experimental procedure has three parts:
training, prediction and evaluation.
For training, we take a sample of network trace traffic and attempt to recover the model hypothesized in \Section{hypothesis} from it.
We use the trained model to predict behaviors of a separate set of flows from the same trace, using only knowledge of a few initial packets of each flow.
Finally, we must evaluate the quality of these predictions by comparing them to the actual behavior of those flows.
In this section we present the methodology for training and prediction;
how to evaluate prediction results against actual behavior is left until the next section together with the results.

% It seems wise at this point to address the nature of prediction for highly nondeterministic phenomena like network traffic.
% Brief reflection shows that one cannot hope to accurately predict the exact behavior of flows:
% flows may exhibit the same initial behavior but subsequently behave quite differently.
% The best we can do then is to predict a \emph{distribution} of possible outcomes given the observed initial behavior.
% When compared with a specific outcome, such a prediction cannot be said to be ``wrong'' or ``right.''
% How then can one measure the quality of a predicted distribution of outcomes?
% This subtle and difficult issue is central to our evaluation methodology.
